HPC--101\\Onboarding

### 2020-01-18 hpc_101/sections/03_policies.tex
comment out a policy
Addition of a security section

\begin{frame}
\frametitle{Where to find all UH-HPC specific policies}
\begin{enumerate}
\item \href{http://www.hawaii.edu/infotech/policies/itpolicy.html\#appendixa}{Chapter 708, Hawaii Revised Statutes}
\item \href{http://www.hawaii.edu/infotech/policies/itpolicy.html}{University of Hawaii Executive Policy E2.210}
\item \href{http://go.hawaii.edu/GSY}{Common systems \& Storage}
\item \href{http://go.hawaii.edu/0SG}{User Account life cycle}
\item \href{http://go.hawaii.edu/WSG}{Security}
\item \href{http://go.hawaii.edu/YKG}{For lease storage}
\item \href{http://go.hawaii.edu/GK0}{Condo Program \& Off Warranty condo nodes}
\item \href{https://docs.google.com/document/d/1mGcCAsmzGT_hWXLcUNfT2LUwiggCnhqrln32k0IGZZI/}{Special allocations}
\end{enumerate}
\end{frame}
%
%\begin{frame}
%\frametitle{Login Node Usage Policy}\footnotesize
%The login nodes are a shared resource and are the only access to the cluster for hundreds of user and are meant to provide the following functionality for all users: 
%\begin{itemize}
%\item Providing ssh shell access 
%\item Facilitate the transfer files to and from the cluster:\\Globus, sftp, scp, rsync
%\item Launching and monitoring SLURM jobs (batch and interactive)
%\item Modifying text files with a text editor: vi/vim, emacs, nano
%\end{itemize}
%\bigskip
%\begin{itemize}
%\item[--] If we identify or are notified that a user is running computation on the login nodes, the application will be killed
%\item[--] If we determine that a user repeatedly violates the login node policy, even after being warned, the repeat offender can have their cluster account disabled
%\end{itemize}
%\btVFill
%\begin{center}
%\footnotesize \textbf{\emph{Login node usage policy is subject to change~\\Users will be notified via email prior to changes taking effect}}
%\end{center}
%\end{frame}
%
%
%\subsection{Lustre Filesystem Purge Policies}
%\begin{frame}
%\frametitle{{\lustre} Filesystem Purge Policies}
%Due to users not having any quotas on the {\lustre} filesystem, we need some policy in place which removes older files from the system.  To accomplish this, we have implemented a purge policy.
%
%\begin{itemize}
%\item What in \ctilde/lus/ is subject to the purge policy?
   %\begin{itemize}
   %\item \textbf{Answer:} Everything but directories.
   %\end{itemize}
%\item When will my files be purged?
  %\begin{itemize}  
    %\item \textbf{Answer:} Files greater than or equal to 1 Megabyte in size or are empty (0 bytes) that are 35 days old
    %\item \textbf{Answer:} Files between 1 byte and 1 Megabyte in size that are 120 days old
  %\end{itemize}
%\item What is the age based on?
   %\begin{itemize}
   %\item \textbf{Answer:} Age of file is based on creation time
   %\end{itemize}
   %
%%\item How frequently are files for purged?
%%   \begin{itemize}
%%   \item \textbf{Answer:} Taking into account the fill rate of the {\lustre} filesystem, a purge is performend as usage approaches 80\%.
%%   \end{itemize}
%\end{itemize}
%\btVFill
%\begin{center}
%\footnotesize \textbf{\emph{Purge policy is subject to change~\\Users will be notified via email prior to changes taking effect}}
%\end{center}
%\end{frame}
%
%
%
%\begin{frame}
  %\frametitle{How to check file age for purge}
  %A tool is available on the cluster called age\_check.  This tool will list all files that are older than the defined date you set.
%\begin{semiverbatim}\tiny \texttt
  %$[$root@login-0001 \ctilde$]$\$ age\_check -h
  %
  %Usage:
  %age\_check [-s] [-z] [-d] [-f] [-a <age cutoff>] [-p <path]
%
%
  %Options:
%
  %-s -- Sort output
  %
  %-d -- display creation date per file
  %
  %-z -- display size in bytes per file
  %
  %-f -- Do not exclude files between 1 byte and 1 MB
  %
  %-a age -- Lists files that were created at least age days ago (default is 20 days)
  %
  %-p path -- Directory to check in (default is /lus/scratch/root)
%
  %
  %Example:
  %age\_check -a 30  
%
%\end{semiverbatim}
%
%\end{frame}

>>>>

\begin{frame}
\frametitle{Where to find all UH-HPC specific policies}
\begin{enumerate}
%\item \href{http://www.hawaii.edu/infotech/policies/itpolicy.html\#appendixa}{Chapter 708, Hawaii Revised Statutes}
%\item \href{http://www.hawaii.edu/infotech/policies/itpolicy.html}{University of Hawaii Executive Policy E2.210}
\item \href{http://go.hawaii.edu/GSY}{Common systems \& Storage}
\item \href{http://go.hawaii.edu/0SG}{User Account life cycle}
\item \href{http://go.hawaii.edu/WSG}{Security}
\item \href{http://go.hawaii.edu/YKG}{For lease storage}
\item \href{http://go.hawaii.edu/GK0}{Condo Program \& Off Warranty condo nodes}
%% \item \href{https://docs.google.com/document/d/1mGcCAsmzGT_hWXLcUNfT2LUwiggCnhqrln32k0IGZZI/}{Special allocations}
\end{enumerate}
\end{frame}
%
%\begin{frame}
%\frametitle{Login Node Usage Policy}\footnotesize
%The login nodes are a shared resource and are the only access to the cluster for hundreds of user and are meant to provide the following functionality for all users: 
%\begin{itemize}
%\item Providing ssh shell access 
%\item Facilitate the transfer files to and from the cluster:\\Globus, sftp, scp, rsync
%\item Launching and monitoring SLURM jobs (batch and interactive)
%\item Modifying text files with a text editor: vi/vim, emacs, nano
%\end{itemize}
%\bigskip
%\begin{itemize}
%\item[--] If we identify or are notified that a user is running computation on the login nodes, the application will be killed
%\item[--] If we determine that a user repeatedly violates the login node policy, even after being warned, the repeat offender can have their cluster account disabled
%\end{itemize}
%\btVFill
%\begin{center}
%\footnotesize \textbf{\emph{Login node usage policy is subject to change~\\Users will be notified via email prior to changes taking effect}}
%\end{center}
%\end{frame}
%
%
%\subsection{Lustre Filesystem Purge Policies}
%\begin{frame}
%\frametitle{{\lustre} Filesystem Purge Policies}
%Due to users not having any quotas on the {\lustre} filesystem, we need some policy in place which removes older files from the system.  To accomplish this, we have implemented a purge policy.
%
%\begin{itemize}
%\item What in \ctilde/lus/ is subject to the purge policy?
   %\begin{itemize}
   %\item \textbf{Answer:} Everything but directories.
   %\end{itemize}
%\item When will my files be purged?
  %\begin{itemize}  
    %\item \textbf{Answer:} Files greater than or equal to 1 Megabyte in size or are empty (0 bytes) that are 35 days old
    %\item \textbf{Answer:} Files between 1 byte and 1 Megabyte in size that are 120 days old
  %\end{itemize}
%\item What is the age based on?
   %\begin{itemize}
   %\item \textbf{Answer:} Age of file is based on creation time
   %\end{itemize}
   %
%%\item How frequently are files for purged?
%%   \begin{itemize}
%%   \item \textbf{Answer:} Taking into account the fill rate of the {\lustre} filesystem, a purge is performend as usage approaches 80\%.
%%   \end{itemize}
%\end{itemize}
%\btVFill
%\begin{center}
%\footnotesize \textbf{\emph{Purge policy is subject to change~\\Users will be notified via email prior to changes taking effect}}
%\end{center}
%\end{frame}
%
%
%
%\begin{frame}
  %\frametitle{How to check file age for purge}
  %A tool is available on the cluster called age\_check.  This tool will list all files that are older than the defined date you set.
%\begin{semiverbatim}\tiny \texttt
  %$[$root@login-0001 \ctilde$]$\$ age\_check -h
  %
  %Usage:
  %age\_check [-s] [-z] [-d] [-f] [-a <age cutoff>] [-p <path]
%
%
  %Options:
%
  %-s -- Sort output
  %
  %-d -- display creation date per file
  %
  %-z -- display size in bytes per file
  %
  %-f -- Do not exclude files between 1 byte and 1 MB
  %
  %-a age -- Lists files that were created at least age days ago (default is 20 days)
  %
  %-p path -- Directory to check in (default is /lus/scratch/root)
%
  %
  %Example:
  %age\_check -a 30  
%
%\end{semiverbatim}
%
%\end{frame}

### 2020-01-18 hpc_101/sections/04_security.tex
Addition of a security section

\begin{frame}
  \frametitle{Goals of data governance @ UH}  
  \begin{itemize}
  \item Protect the privacy and security of ``Protected Data''
    \begin{itemize}
    \item All non-public data
    \item Institutional data
    \item Research data
    \end{itemize}
  \item Produce higher quality data for informed decision making
  \item Promote efficient use of resources
  \item Increase transparency and accountability
  \end{itemize}
\end{frame}

\subsection{Data Classifications @ UH}
\begin{frame}
  \frametitle{Data Classifications @ UH}
  \vspace{-5pt}
  \makebox[\linewidth][c]{
    \resizebox{\textwidth}{!}{%
      \begin{tabular}{l||p{6cm}||p{6cm}}
      %  \multicolumn{8}{c}{ {\large {\textbf{UH-HPC Resource Summary} } } } \\ 
	\toprule                                                                    
        \thead{\large\textbf{Category}} & \thead{\large\textbf{Definition}} & \thead{\large\textbf{Examples}} \\ 
	\midrule  \midrule %\hline
        \textbf{Public} & Access is not restricted and is subject to open records requests  & Student directory information, employee’s business contact info \\
	\midrule  \midrule %\hline
        \multicolumn{3}{c}{ {\large {\textbf{Protected Data} } } } \\ 
	\midrule  \midrule %\hline
        \textbf{Restricted} & Used for UH business only; will not be distributed to external parties; released externally only under the terms of a written MOA or contract & Student contact information, UH ID number \\
	\midrule  
        \textbf{Sensitive} & Data subject to privacy considerations  & Date of birth, job applicant records, salary/payroll information, most student information \\
	\midrule  
        \textbf{Regulated} & Inadvertent disclosure or inappropriate access requires a breach notification by law or is subject to financial fines & FN or first initial/LN in combination with SSN, driver license number, or bank information; credit card, HIPAA, or financial aid information \\            
    \bottomrule
      \end{tabular}%
    }    }
  \vspace{-5pt}
  \begin{block}{Protected Data}
    Collecting, managing, sharing or using  data that can be classified in a protected data category the Data Governance Process (DGP) is required 
  \end{block}
\end{frame}

@@

    \item \href{Health Insurance Portability and Accountability Act (https://www.hhs.gov/hipaa/for-professionals/security/laws-regulations/index.html}{HIPPA}) [UH Policy \href{https://www.hawaii.edu/policy/index.php?action=viewPolicy\&policySection=ep\&policyChapter=2\&policyNumber=217\&menuView=closed}{EP 2.217}]
      \begin{itemize}
      \item Federal law that protects the privacy of health information
        \item \href{https://www.hawaii.edu/infosec/hipaa/}{HIPPA @ UH}
      \end{itemize}
    \end{itemize}  
  \end{block}
\end{frame}

@@

\subsection{State Regulations}
\begin{frame}
  \frametitle{Regulations}
  \vspace{-5pt}
  \begin{block}{State Regulations}
    \begin{itemize}
    \item \href{https://www.capitol.hawaii.gov/hrscurrent/Vol11_Ch0476-0490/HRS0487N/HRS_0487N-.htm}{{\hawaii} Revised Statues (HRS) 487N}
      \begin{itemize}
      \item State law that defines the breach notification to the legislature
      \item Examples: First name or First initial and Last name in combination with
        \begin{itemize}
        \item Social Security Number (SSN)
        \item Driver license or State ID \#
        \item Person's finanical account information
          \end{itemize}
      \end{itemize}

@@

\section{UH Data Related Policies \& Procedures}
\begin{frame}
  \frametitle{UH Data Related Policies \& Procedures}
  \vspace{-7pt}
\makebox[\linewidth][c]{
    \resizebox{\textwidth}{!}{%                                                                                                                                                                                                                                                       
      \begin{tabular}{l||l}
      %  \multicolumn{8}{c}{ {\large {\textbf{UH-HPC Resource Summary} } } } \\                                                                                                                                                                                                       
        \toprule
        \thead{\large\textbf{Policy}} & \thead{\large\textbf{Description}} \\
        \midrule  \midrule %\hline
        \multicolumn{2}{c}{ {\large {\textbf{Administrative Procedure} } } } \\  
        \midrule \midrule
        \textbf{AP2.215} & Mandatory Training \& Continuing Education Requirements \\
        \midrule
        \textbf{AP7.022} & FERPA \\
        \midrule \midrule
        \multicolumn{2}{c}{ {\large {\textbf{Executive Policy} } } } \\  
        \midrule \midrule
        \href{https://www.hawaii.edu/policy/?action=viewPolicy\&policySection=ep\&policyChapter=2\&policyNumber=210\&menuView=closed}{\textbf{EP2.210}} & Use and Management of Information Technology Resources \\
        \midrule
        \href{}{\textbf{EP2.213}} & System and Campus Wide Electronic Channels for Communicating with Students\\
        \midrule        
        \textbf{EP2.214} & Data Classification Categories \& Information Security Guidelines \\
        \midrule
        \textbf{EP2.215} & Institutional Data Governance \\
        \midrule
        \textbf{EP2.216} & Institutional Records Management \& Electronic Approvals/Signatures (\textit{Pending Approval}) \\
        \midrule
        \textbf{EP2.217} & HIPPA (\textit{To be Revised}) \\
        \midrule
        \textbf{EP2.218} & Online Approvals of Internal University Transactions\\
        \midrule
        \textbf{EP2.2xx} & Student Online Data Protection Requirements (\textit{Draft}) \\
        \midrule
        \textbf{EP2.215} & Institutional Data Governance \\
        \midrule
        \textbf{EP8.200} & Policy on Contracts \& Signing Authority \\
        \bottomrule
      \end{tabular}%
      }
}
\vspace{-5pt}

@@

>>>>

\begin{frame}
  \frametitle{Goals of data governance @ UH}
  \begin{block}{}
    \href{https://www.hawaii.edu/offices/vp-academic-planning-policy/uh-institutional-data-governance/}{The Data Governance Office at the University of {\hawaii}} creates policies and procedures focused on the privacy and security of data under the University’s care. 
  \end{block}
  \begin{block}{Goals}
  \begin{itemize}
  \item Protect the privacy and security of ``Protected Data''
    \begin{itemize}
    \item All non-public data
    \item Institutional data
    \item Research data
    \end{itemize}
%  \item Produce higher quality data for informed decision making
  \item Promote efficient use of resources
  \item Increase transparency and accountability
  \end{itemize}
  \end{block}
\end{frame}

\subsection{Data Classifications @ UH}
\begin{frame}
  \frametitle{Data Classifications @ UH}
  \vspace{-5pt}
  \makebox[\linewidth][c]{
    \resizebox{\textwidth}{!}{%
      \begin{tabular}{l||p{6cm}||p{6cm}}
      %  \multicolumn{8}{c}{ {\large {\textbf{UH-HPC Resource Summary} } } } \\ 
	\toprule                                                                    
        \thead{\large\textbf{Category}} & \thead{\large\textbf{Definition}} & \thead{\large\textbf{Examples}} \\ 
	\midrule  \midrule %\hline
        \textbf{Public} & Access is not restricted and is subject to open records requests  & Student directory information, employee’s business contact info \\
	\midrule  \midrule %\hline
        \multicolumn{3}{c}{ {\large {\textbf{Protected Data} } } } \\ 
	\midrule  \midrule %\hline
        \textbf{Restricted} & Used for UH business only; will not be distributed to external parties; released externally only under the terms of a written MOA or contract & Student contact information, UH ID number \\
	\midrule  
        \textbf{Sensitive} & Data subject to privacy considerations  & Date of birth, job applicant records, salary/payroll information, most student information \\
	\midrule  
        \textbf{Regulated} & Inadvertent disclosure or inappropriate access requires a breach notification by law or is subject to financial fines & FN or first initial/LN in combination with SSN, driver license number, or bank information; credit card, HIPAA, or financial aid information \\            
    \bottomrule
      \end{tabular}%
    }    }
  \vfill
  \centering
    The \href{https://datagov.intranet.hawaii.edu/dgp/}{Data Governance Process (DGP)} applies to collecting, managing, sharing or using data that can be classified as protected data
\end{frame}

@@

    \item \href{https://www.hhs.gov/hipaa/for-professionals/security/laws-regulations/index.html}{Health Insurance Portability and Accountability Act (HIPPA}) [UH Policy \href{https://www.hawaii.edu/policy/index.php?action=viewPolicy\&policySection=ep\&policyChapter=2\&policyNumber=217\&menuView=closed}{EP 2.217}]
      \begin{itemize}
      \item Federal law that protects the privacy of health information
        \item \href{https://www.hawaii.edu/infosec/hipaa/}{HIPPA @ UH}
      \end{itemize}
    \end{itemize}  
  \end{block}
\end{frame}

@@

\subsection{State Regulations}
\begin{frame}
  \frametitle{Regulations}
  \vspace{-5pt}
  \begin{block}{State Regulations}
    \begin{itemize}
    \item \href{https://www.capitol.hawaii.gov/hrscurrent/Vol11_Ch0476-0490/HRS0487N/HRS_0487N-.htm}{{\hawaii} Revised Statues (HRS) 487N}
      \begin{itemize}
      \item State law that defines the breach notification to the legislature
      \item Examples: First name or First initial and Last name in combination with at least one of the following
        \begin{itemize}
        \item Social Security Number (SSN)
        \item Driver license or State ID \#
        \item Person's finanical account information
          \end{itemize}
      \end{itemize}

@@

\subsection{UH Data Related Policies \& Procedures}
\begin{frame}
  \frametitle{UH Data Related Policies \& Procedures}
  \vspace{-7pt}
\makebox[\linewidth][c]{
    \resizebox{\textwidth}{!}{%                                                                                                                                                                                                                                                       
      \begin{tabular}{l||l}
      %  \multicolumn{8}{c}{ {\large {\textbf{UH-HPC Resource Summary} } } } \\                                                                                                                                                                                                       
        \toprule
        \thead{\large\textbf{Policy}} & \thead{\large\textbf{Description}} \\
        \midrule  \midrule %\hline
        \multicolumn{2}{c}{ {\large {\textbf{Administrative Procedure} } } } \\  
        \midrule \midrule
        \href{https://www.hawaii.edu/policy/?action=viewPolicy\&policySection=ap\&policyChapter=2\&policyNumber=215\&menuView=closed}{\textbf{AP2.215}} & Mandatory Training \& Continuing Education Requirements \\
        \midrule
        \href{https://www.hawaii.edu/policy/?action=viewPolicy\&policySection=ap\&policyChapter=7\&policyNumber=022\&menuView=closed}{\textbf{AP7.022}} & FERPA \\
        \midrule \midrule
        \multicolumn{2}{c}{ {\large {\textbf{Executive Policy} } } } \\  
        \midrule \midrule
        \href{https://www.hawaii.edu/policy/?action=viewPolicy\&policySection=ep\&policyChapter=2\&policyNumber=210\&menuView=closed}{\textbf{EP2.210}} & Use and Management of Information Technology Resources \\
        \midrule
        \href{https://www.hawaii.edu/policy/?action=viewPolicy\&policySection=ep\&policyChapter=2\&policyNumber=213\&menuView=closed}{\textbf{EP2.213}} & System and Campus Wide Electronic Channels for Communicating with Students\\
        \midrule        
        \href{https://www.hawaii.edu/policy/?action=viewPolicy\&policySection=ep\&policyChapter=2\&policyNumber=214\&menuView=closed}{\textbf{EP2.214}} & Data Classification Categories \& Information Security Guidelines \\
        \midrule
        \href{https://www.hawaii.edu/policy/?action=viewPolicy\&policySection=ep\&policyChapter=2\&policyNumber=215\&menuView=closed}{\textbf{EP2.215}} & Institutional Data Governance \\
        \midrule
        \href{https://www.hawaii.edu/policy/?action=viewPolicy\&policySection=ep\&policyChapter=2\&policyNumber=216\&menuView=closed}{\textbf{EP2.216}} & Institutional Records Management \& Electronic Approvals/Signatures (\textit{Pending Approval}) \\
        \midrule
        \href{https://www.hawaii.edu/policy/?action=viewPolicy\&policySection=ep\&policyChapter=2\&policyNumber=217\&menuView=closed}{\textbf{EP2.217}} & HIPPA (\textit{To be Revised}) \\
        \midrule
        \href{https://www.hawaii.edu/policy/?action=viewPolicy\&policySection=ep\&policyChapter=2\&policyNumber=218\&menuView=closed}{\textbf{EP2.218}} & Online Approvals of Internal University Transactions\\
        \midrule
        \textbf{EP2.2xx} & Student Online Data Protection Requirements (\textit{Draft}) \\
        \midrule
        \href{https://www.hawaii.edu/policy/?action=viewPolicy\&policySection=ep\&policyChapter=2\&policyNumber=215\&menuView=closed}{\textbf{EP2.215}} & Institutional Data Governance \\
        \midrule
        \href{https://www.hawaii.edu/policy/?action=viewPolicy\&policySection=ep\&policyChapter=8\&policyNumber=200\&menuView=closed}{\textbf{EP8.200}} & Policy on Contracts \& Signing Authority \\
        \bottomrule
      \end{tabular}%
      }
}
\vspace{-5pt}

@@

\section[Security]{Security}

\subsection{Information Security Program}
\begin{frame}
  \frametitle{Information Security Program}

  The \href{https://www.hawaii.edu/infosec/infosecprogram/}{University of {\hawaii} Information Security Program} is comprised of the following strategic areas:

  \begin{block}{Strategic Areas}
    \begin{itemize}
  \item Data Governance \& Oversight
  \item Information Security Audits \& Risk Assessments
  \item Information Security Policies \& Procedures
  \item Identity Management \& Access Controls
  \item Information Security Training \& Awareness
  \end{itemize}
  \end{block}
\end{frame}

\subsection{Data Protection}
\begin{frame}
  \frametitle{Protect Your Data!}
  \vspace{-10pt}
  \begin{block}{Know which files have sensitive information}
    \begin{itemize}
    \item Use \href{http://www.hawaii.edu/askus/1297}{Spirion} (formerly Identity Finder) to scan for sensitive information
    \end{itemize}
  \end{block}
  \vspace{-3pt}  
  \begin{block}{Protect sensitive/regulated data as required by UH policy}
  \begin{itemize}
  \item UH Policy \href{https://www.hawaii.edu/policy/EP2.214}{EP 2.214}
  \end{itemize}
  \end{block}
  \vspace{-3pt}  
  \begin{block}{Data protection life cycle}
    \begin{itemize}
    \item Back up your data regularly
    \item Transmit and share sensitive data in a secure manner, e.g., SFTP, \href{https://www.hawaii.edu/filedrop/}{UH FileDrop}
    \item Protect sensitive/regulared data with encryption
    \item Securely delete any sensitive data that is no longer needed
    \end{itemize}
  \end{block}    
  \vspace{-3pt}  
  \begin{block}{Physical Security of data repository with sensitive data}
    \begin{itemize}
    \item Paper documents should be stored in a secured location, not accessible by unauthorized individuals e.g., a locked file cabinent
    \item External hard drives should be stored in a secured location e.g., a locked file cabinent
    \end{itemize}
  \end{block}    
\end{frame}

\subsection{Device Protection}
\begin{frame}
  \frametitle{Protect Your Computers!}
  \begin{block}{Operating System (OS) }
    \begin{itemize}
    \item Apply updates to your OS and applications frequently and on a regular basis
    \end{itemize}
  \end{block}

  \begin{block}{Protective Software}
  \begin{itemize}
  \item Install and keep up to date protective software such as \href{http://www.hawaii.edu/askus/1254}{anti-virus}
  \end{itemize}
  \end{block}

  \begin{block}{Physical Access}
    \begin{itemize}
    \item Never leave your devices logged-in \& unattended
    \item Control physical access to your machines
    \item When you step away from your machine, lock your screen
    \item Require password authentication when unlocking or accessing your machine
    \end{itemize}
  \end{block}    
\end{frame}

\subsection{Storing and transmitting data with Google products}
\begin{frame}
  \frametitle{Storing and transmitting data with Google products}
  \onslide<1->{\begin{block}{Question}
    \begin{columns}[T ]
      \begin{column}{0.15\textwidth}\hfill\includegraphics[scale=0.05]{question_mark.png}\end{column}
      \begin{column}{0.80\textwidth}
        Is it safe to store and transmit sensitive or regulated data using the different Google products offerred at the University?
        e.g., Google Docs, Google Drive, Gmail
      \end{column}
    \end{columns}
    \end{block}
    }
  \vfill
  \onslide<2->{\begin{block}{Answer}
%https://www.kissclipart.com/stop-hand-clipart-stop-sign-clip-art-pgay2w/
\begin{columns}
\begin{column}{0.15\textwidth}\hfill\includegraphics[scale=0.05]{stop_hand.png}\end{column}
\begin{column}{0.70\textwidth}
    \centering
    {\HUGE \textbf{\textit{NO!}}}\Large~\\Do \textbf{NOT} store or transmit sensitive or regulated information in \emph{Google Docs}, \emph{Google Drive} or \emph{Email}!
\end{column}
\begin{column}{0.15\textwidth}\includegraphics[scale=0.05]{stop_hand.png}\end{column}
\end{columns}
    \end{block}}
\end{frame}

\subsection{Account protection}
\begin{frame}
  \frametitle{Protect Your Account!}
\begin{columns}
\begin{column}{0.45\textwidth}
\begin{block}{}
  \begin{itemize}
  \item User strong passwords and a strong password management strategy
  \item \textbf{DO NOT RE-USE PASSWORDS!}
  \item Consider using a passphrase
    \begin{itemize}
    \item lower/uppercase
    \item numbers
    \item special characters
    \item character substitutions, e.g.,
      \begin{itemize}
      \item o $\Longrightarrow$ 0
      \item a $\Longrightarrow$ @
      \item i $\Longrightarrow$ 1
      \end{itemize}
    \end{itemize}
  \item Check your password strength: \href{https://lastpass.com/howsecure.php}{https://lastpass.com/howsecure.php}
  \item Monitor your accounts for suspicious activity
  \end{itemize}
  \end{block}
\end{column}
\begin{column}{0.49\textwidth}
\begin{block}{}
  \includegraphics[scale=0.25]{password_strength.png}
  \numlessfootnotetxt{\label{xkcd_pasword_strnght}\tiny\url{https://xkcd.com/936/}}
\end{block}
\end{column}
\end{columns}
\end{frame}

\section*{More Information}
\begin{frame}
  \frametitle{More Information}
  You can find more information about Data Governance and Security at UH at the following links:
  \begin{itemize}
  \item \href{https://datagov.intranet.hawaii.edu/}{Data Governance internal site}
  \item \href{https://datagov.intranet.hawaii.edu/training/}{Data Governance \& Security trainings/presentations}
  \item \href{https://datagov.intranet.hawaii.edu/institutional-data-classification-levels/}{Institutional data classifications}
  \item \href{https://www.hawaii.edu/infosec/}{Information Security (InfoSec) at UH}
  \item \href{https://www.hawaii.edu/its/alerts/}{Security notices and other alerts from UH Information Technology Services (ITS)}
  \item \href{https://www.hawaii.edu/its/itacw/}{IT All Campus Workshop \ddash Yearly during the summer}
  \end{itemize}
\end{frame}
